Meaning of simple rules in investment strategies of algorithmic trading

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
beliving of drawdown trend

Conversely in quarters, c) and d) the first movement of the market is declining and investor reaction is recorded appropriately in decisions (4) and (5). In quarter c) investor behaves as if he predicts horizontal trend and opens long position (4) and in quarter d) in believe of drowdown trend he opens short position (5). \\

>>>>

Conversely in quarters, c) and d) the first movement of the market is declining and investor reaction is recorded appropriately in decisions (4) and (5). In quarter c) investor behaves as if he predicts horizontal trend and opens long position (4) and in quarter d) beliving of drawdown trend he opens short position (5). \\
